---
title: "Tidy and join tables"
format: html
---

# Instructions

This week, you learned about the concept of tidy data and practiced reshaping data with functions from the `tidyr` package. You also learned to join tables with `dplyr` functions.

You'll use those skills to combine the `credit_personal` data set with a new data set containing financial information for credit applicants.

To learn more about the variables contained in the data set(s), refer to the data dictionary: https://rsacdn.link/milestones/internal/v2/tidyverse/credit-risk/assets/credit-risk_dictionary.html

Remember that all tidyverse packages have already been installed for you but you will need to *load* the ones you want to use.

# Milestone

```{r}
#| label: setup
#| include: false

# Load your packages here

```

## Tidy and join

In this milestone you'll add financial information about applicants to the `credit_personal` data set you have been working with. You have a new file in the `data/` folder your working directory that you will need to use: `credit_financial.csv`.

### Part 1 - Import

Before you begin, you will need to import your data sets. Use the code chunk below to read two data sets from the `data/` directory:

1. `credit_personal.csv`, save it as `credit_personal`
2. `credit_financial.csv`, save it as `credit_financial`

```{r}
#| label: recreation-import

```

### Part 2 - Join tables

Run the code below to see a table.

```{r}
#| label: recreate-this
#| message: false
solution <- readr::read_csv("data/milestone04.csv")
solution
```

This table shows both personal and financial information for credit applicants. Your task is to recreate the table by joining the data in `credit_personal.csv` with `credit_financial.csv`.

You will need to do some pre-join checks:

1. Which variables can you join on?
2. Do the data sets have any mismatched observations?
3. Perform any necessary data cleaning.
4. Check again as needed!

Then, join the cleaned data sets.

Write your code in the chunk below. Save the result as `credit_full`.

```{r}
#| label: recreation

```

To test whether you have the same answer as the solution, run the following code chunk:

```{r}
#| label: compare
#| eval: false
#| message: false

waldo::compare(
  credit_full,
  solution,
  tolerance = 1e-4,
  ignore_attr = c("class", "groups")
)
```

### Part 3 - Summarize and visualize

Using the File Explorer, navigate to the `images/` directory, then click on `milestone04.png` to open an image.

You should see a plot that displays the average credit amount by credit history type.

Recreate the plot using your solution table (`credit_full`) from above.

You will need to:

1. Find the average credit for each type of `credit_history`

2. Use `ggplot()` to reproduce the plot

```{r}
#| label: recreation-2

```

## Extension

Using the code chunk below, investigate a research question about this data, using the skills you have learned this week and in previous weeks of Academy. Try to make use of variables from both `credit_personal` and `credit_financial`. Some ideas:

1. Do applicants with more dependents tend to have more existing lines of credit, and is this different for different marital statuses?
2. Are foreign workers more likely to be classified as "good" credit than non-foreign workers; and is this relationship different depending on the type of job they have?
3. Do larger credit amounts tend to have longer duration and/or a larger number of installments?
4. [any other research question of interest]

Alternately, working with a data set of your own, complete the following:

1. Read in your data
2. Complete a data wrangling task relevant to your data (tidying and/or reshaping/pivoting your data); if appropriate, join your data with a second data set (filtering or mutating join)
3. Show summary tables of your data throughout these transformations


```{r}
#| label: extension

```
