---
title: "Wrangle rows and columns"
format: html
---

# Instructions

This week, you learned several more functions from the dplyr package (pronounced DEE-ply-er). These functions help you work with the rows and columns in your data set.

You'll use these skills to investigate how employment relates to credit amounts.

To learn more about the variables contained in the data set, refer to the data dictionary: https://rsacdn.link/milestones/internal/v2/credit-risk/assets/credit-risk_dictionary.html

# Milestone

```{r}
#| label: setup
#| include: false

# Load your packages here

```

## Create and select columns

This week, you'll calculate the average credit amount for skilled worker applicants, grouped by length of employment.

## Recreation

### Part 1 - Import

Before you begin, you will need to import your data set. Use the code chunk below to read the data from the data file `credit_personal.csv`, which is stored in the `data/` folder in your working directory. Be sure to save the data to an object named `credit_personal`.

```{r}
#| label: recreation-import

```

### Part 2 - Create

Run the chunk below to see a table.

```{r}
#| label: recreate-this
#| message: false
solution <- readr::read_csv("data/milestone03.csv")
solution
```

Use `credit_personal` to recreate this table displaying the average credit amount (specifically the mean amount) grouped by how long the applicant has been employed, for skilled workers only.

You will need to:

1. Limit your data set to only the "skilled" job type.

2. Use `mutate()` and `case_when()` to make a new variable called `employment_length`, which uses categories of the existing `employment` variable to determine if applicants were employed for more or less than 4 years.

3. Find the mean credit awarded for each category of `employment_length`.

4. Sort the rows in increasing order of mean credit


Write your code in the chunk below. Store your result in an object called `credit_summary_employment`.

```{r}
#| label: recreation

```

To test whether you have the same answer as the solution, run the following code chunk. Note that we're using the `tolerance` argument in the `waldo::compare()` function to ignore minor differences in rounding error.

```{r}
#| label: compare
#| eval: false
#| message: false

waldo::compare(
  credit_summary_employment,
  solution,
  tolerance = 1e-4
)
```

## Extension

For your extension, consider addressing one of the following research questions with a table and/or plot:

1. What is the relationship between amount of savings and age? (Hint: Decide how you will make a new variable from `savings_status` to address this question.)
2. Do applicants who own their home tend to have lived there longer (`residence_since`) than applicants who rent?
3. Is there a relationship between applicants' decade of age (e.g. 20s, 30s, 40s) and the average amount of credit awarded?
4. [any other research question of interest]

Alternately, working with a data set of your own, complete the following:

1. Read in your data
2. Create at least one new variable in your data set (using `mutate()` and/or `summarize()`), or use other dplyr functions to alter your data
3. Use your updated data set to create at least one graph and/or table

```{r}
#| label: extension

```
