---
title: "Work with data types"
format: html
---

# Instructions

This week, you worked with three new data types in R -- factors, strings, and date-times -- using the forcats, stringr, and lubridate packages, respectively.

In this milestone, you'll further tidy the joined data set from Milestone 4 using stringr functions. Then, you'll visualize the tidied data set using tools from ggplot2.

To learn more about the variables contained in the data set, refer to the data dictionary: https://rsacdn.link/milestones/internal/v2/tidyverse/credit-risk/assets/credit-risk_dictionary.html

# Milestone

## Data types

In this milestone, you'll start with the joined data set from Milestone 4.

First, you'll use stringr functions to clean the values of several variables in the data set. Then, you'll recreate a plot using ggplot2.

### Part 1 - Import and join

Run the chunk below to repeat the steps from Milestone 4, creating the `credit_full` data set.

```{r}
#| label: setup
#| include: false

# Run this chunk before starting this milestone
library(tidyverse)

# Read data
credit_financial <- read_csv("data/credit_financial.csv")
credit_personal <- read_csv("data/credit_personal.csv")

# Join personal and financial credit data
credit_full <- left_join(credit_personal, credit_financial, by = "applicant_id")
```

### Part 2 - Strings

Run the following chunk to view a table.

```{r}
#| label: recreate-this-1
#| message: false
solution <- readr::read_csv("data/milestone05.csv")
solution
```

Your task is to recreate this table using `credit_full`. Try to use the `stringr` package for these adjustments, *not* `case_when()` or `if_else()`.

For this recreation, you'll need to:

1. Split the `personal_status` column into two new columns, `sex` and `marital_status`.

2. Make a new column called `previous_delay`, based on whether or not the credit history of the applicant included late payment. (Hint: the categories of `credit_history` that include the word "paid" are the ones without late payments.)

3. Keep only the columns shown in the solution table, in the order they appear in that solution.

Write your code in the following chunk. Save the result to an object called `credit_full_clean`.

```{r}
#| label: recreation-1

```

To test whether you have the same answer as the solution, run the following code chunk:

```{r}
#| label: compare
#| eval: false
#| message: false

waldo::compare(
  credit_full_clean,
  solution,
  tolerance = 1e-4
)
```

### Part 3 - Visualize

Using the File Explorer, navigate to the `images/` directory, then click on `milestone05.png` to open an image.

You should see a plot that displays applicant credit history by marital status.

Use the `credit_full_clean` object from Part 2 to recreate this plot. *Hint:* Notice the order of the bars on the x axis -- before plotting, use a forcats function to turn the `marital_status` variable into a factor with a set order.

Write your code in the following chunk:

```{r}
#| label: recreation-2

```

## Extension

For your extension, consider further refining the `credit_full_clean` data set using your knowledge of string data. For example, you might:

1. Combine the `housing` variable and the `property_magnitude` variables into one; for example, "rent" and "life insurance" could become "rents housing; has life insurance".
2. Make a *numeric* column called `approx_savings` which includes the maximum, minimum, or average value for the range given by the `savings_status` category. For example, the category "100<X<500" could be converted to "100" or "300" or "500".
3. Similarly, make a numeric column for the `employment` variable or the `checking_status` variable.

Or, instead, you can make a new visualization to address a more complex research question than we have in previous milestones.

Alternately, working with a data set of your own, complete the following:

1. Read in your data
2. If your data contains ...
  ... date-time data, use a lubridate function to correctly format your date-time variables
  ... string data, use a stringr function to manipulate your string variables
  ... categorical data, use a forcats function to modify the factor levels of your categorical variables (reorder, recode, etc.)
3. Using a table or graph, present a meaningful subset of your modified data

```{r}
#| label: extension

```
