---
title: "Summarize data"
format: html
---

# Instructions

This week, you learned several new functions from dplyr (pronounced DEE-ply-er), a commonly-used package from the tidyverse for wrangling data. You also learned some new ways to enhance your plots.

You'll use these skills to display groupwise summary statistics of credit amounts by job type.

To learn more about the variables contained in the data set, refer to the data dictionary: https://rsacdn.link/milestones/internal/v2/tidyverse/credit-risk/assets/credit-risk_dictionary.html

# Milestone

```{r}
#| label: setup
#| include: false

# Load your packages here

```

## Summarize data

In this milestone, you'll recreate a summary table showing the mean credit amount awarded by job type.

## Recreation

### Part 1 - Import

Before you begin, you will need to import your data set. Use the code chunk below to read the data from the data file `credit_personal.csv`, which is stored in the `data/` folder in your working directory. Be sure to save the data to an object named `credit_personal`.

```{r}
#| label: recreation-import

```

### Part 2 - Summarize and visualize

Run the code below to see a table.

```{r}
#| label: recreate-this
#| message: false
solution <- readr::read_csv("data/milestone02.csv")
solution
```

Your task is to use what you've learned about the dplyr package to transform `credit_personal` into this table. You will need to:

1. Group the data by `job`
2. Summarize the `mean_credit` for each group
3. Use `coord_flip()` to rotate the resulting column plot horizontally

Work in the code chunk below. Save the result as `credit_by_job`.

```{r}
#| label: recreation

```

Run the following code chunk to test whether you have the same answer as the solution:

```{r}
#| label: compare
#| eval: false
waldo::compare(credit_by_job, solution, tolerance = 1e-4)
```

Now create a column plot to visualize the result:

```{r}
#| label: recreation-plot

```

## Extension

Using the code chunk below, investigate a research question about this data, using the data wrangling skills you learned this week. Some ideas:

1. Is there a relationship between a person's job type and marital status, and their personal credit awarded?
2. Is there a relationship between someone's housing payments and foreign worker status, and the amount of credit awarded?
3. Do people tend to be awarded higher credit when they are younger, older, or middle aged?
4. [any other research question of interest]

Alternately, working with a data set of your own, complete the following:

1. Read in your data
2. Use `group_by()` and `summarize()` to produce simple a table from some subset of your data
3. Create a related graph of this data subset using ggplot


```{r}
#| label: extension

```
