---
title: "Credit Risk in Germany"
author: "Your name"
date: today
format: 
  html:
    theme: flatly
    embed-resources: true
    toc: true
    df-print: paged
knitr:
  opts_chunk:
    echo: FALSE
    message: FALSE
    warning: FALSE
---

```{r}
#| label: setup
#| include: false

library(tidyverse)

credit_personal <- readr::read_csv("../data/credit_personal.csv")
```

## Background

The `credit_personal` data set describes the characteristics of German credit applicants. The data come from the [UCI Machine Learning Repository](https://archive.ics.uci.edu/dataset/144/statlog+german+credit+data): 

> This data set classifies people described by a set of attributes as good or bad credit risks. 

```{r}
#| label: data
#| echo: true
credit_personal
```

## Results

We explored how average credit amount varies by applicant job type.

```{r}
#| label: analysis
job_summary <- 
  credit_personal |>
  group_by(job) |>
  summarize(avg_credit_amnt = mean(credit_amount)) |>
  ungroup() 

job_summary
```

```{r}
#| label: computation
job_with_max <- 
  job_summary |> 
  filter(avg_credit_amnt == max(avg_credit_amnt)) |> 
  select(job) |> 
  pull()

max_avg_credit <- 
  job_summary |> 
  filter(avg_credit_amnt == max(avg_credit_amnt)) |> 
  select(avg_credit_amnt) |> 
  pull() |> 
  round(digits = 2)

job_with_min <- 
  job_summary |> 
  filter(avg_credit_amnt == min(avg_credit_amnt)) |> 
  select(job) |> 
  pull()

min_avg_credit <- 
  job_summary |> 
  filter(avg_credit_amnt == min(avg_credit_amnt)) |> 
  select(avg_credit_amnt) |> 
  pull() |> 
  round(digits = 2)
```

On average, applicants with jobs classified as "`r job_with_max`" have the highest average credit amount, at `r max_avg_credit` DM. 

Applicants with jobs classified as "`r job_with_min`" have the lowest average credit amount, at `r min_avg_credit` DM.

```{r}
#| label: figure
job_summary |>
  ggplot(aes(fct_reorder(job, avg_credit_amnt), avg_credit_amnt)) +
  geom_col() +
  labs(
    title = "Average credit amount by job type",
    x = "Job type",
    y = "Average credit amount") + 
  coord_flip() 
```
